%-----------------------------------------------------------------------------------------------------------------------------------------------%
%	The MIT License (MIT)
%
%	Copyright (c) 2021 Jitin Nair
%
%	Permission is hereby granted, free of charge, to any person obtaining a copy
%	of this software and associated documentation files (the "Software"), to deal
%	in the Software without restriction, including without limitation the rights
%	to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%	copies of the Software, and to permit persons to whom the Software is
%	furnished to do so, subject to the following conditions:
%	
%	THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%	IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%	FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%	AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%	LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%	OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN
%	THE SOFTWARE.
%	
%
%-----------------------------------------------------------------------------------------------------------------------------------------------%

%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

% article class because we want to fully customize the page and not use a cv template
\documentclass[a4paper,12pt]{article}

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

% % fontspec allows you to use TTF/OTF fonts directly
% \usepackage{fontspec}
% \defaultfontfeatures{Ligatures=TeX}

% % modified for ShareLaTeX use
% \setmainfont[
% SmallCapsFont = Fontin-SmallCaps.otf,
% BoldFont = Fontin-Bold.otf,
% ItalicFont = Fontin-Italic.otf
% ]
% {Fontin.otf}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip} 	

%other packages for formatting
\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

%tabularx environment
\usepackage{tabularx}

%for lists within experience section
\usepackage{enumitem}

% centered version of 'X' col. type
\newcolumntype{C}{>{\centering\arraybackslash}X} 

%to prevent spillover of tabular into next pages
\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

%custom \section
\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

%for publications
\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

%Setup hyperref package, and colours for links
\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

%for social icons
\usepackage{fontawesome5}

%debug page outer frames
%\usepackage{showframe}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}

% non-numbered pages
\pagestyle{empty} 

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------

% \begin{tabularx}{\linewidth}{ @{}X X@{} }
% \huge{Your Name}\vspace{2pt} & \hfill \emoji{incoming-envelope} email@email.com \\
% \raisebox{-0.05\height}\faGithub\ username \ | \
% \raisebox{-0.00\height}\faLinkedin\ username \ | \ \raisebox{-0.05\height}\faGlobe \ mysite.com  & \hfill \emoji{calling} number
% \end{tabularx}

\begin{tabularx}{\linewidth}{@{} C @{}}
\huge{Daniel Nathan Reis Silva} \\[7.5pt]
\href{https://github.com/danielnatham}{\raisebox{-0.05\height}\faGithub\ danielnatham} \ $|$ \ 
\href{https://www.linkedin.com/in/reis-silva-daniel/}{\raisebox{-0.05\height}\faLinkedin\ reis-silva-daniel} \ $|$ \ 
\href{mailto:danielnatham@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ danielnatham@gmail.com} \\
\\

\end{tabularx}

%----------------------------------------------------------------------------------------
% SUMMARY
%----------------------------------------------------------------------------------------
\section{Summary}

FullStack Software Developer with over 4 years of experience and pursuing a degree in \textbf{Computer Science} at the Federal University of Sergipe.
I have worked on large-scale projects in the \textbf{retail, healthcare, education, and fiscal} sectors, focusing on delivering scalable and secure solutions.

I have solid experience in \textbf{web development} (Java, PHP, JavaScript/TypeScript), as well as integration with fiscal systems (NF-e, NFC-e) and ERPs.
Proficient in relational databases and modern practices of \textbf{DevOps and Cloud} with Docker, CI/CD, and AWS (EC2, ElastiCache, S3, RDS).

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Full Stack Developer} & \hfill Dec. 2024 - Present \\
\textbf{- CD2 Retail Tech}  & \hfill Remote\\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Developed and maintained new features for store management systems and POS, improving efficiency and usability;
            \item[--] Integrated ERPs (such as Bluesoft) and tax systems via SOAP and REST APIs, optimizing data flows and reducing processing time;
            \item[--] Optimized SQL queries, increasing performance of reports and internal processes, significantly reducing generation time;
            \item[--] Updated web and POS interfaces with \textbf{SenchaJS} and \textbf{jQuery}, providing a more modern and fluid user experience;
            \item[--] Performed evolutionary maintenance on SOAP integrations for NF-e and NFC-e, reducing cognitive complexity and improving code quality;
            \item[--] Technologies: \textbf{PHP, jQuery, Oracle, PostgreSQL, SenchaJS, SOAP, REST, JIRA, VueJS}.
        \end{itemize}
    \end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Back End Developer} & \hfill Dec. 2023 - Nov. 2024 \\
\textbf{- SergipeTec}  & \hfill Remote\\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    \begin{minipage}[t]{\linewidth}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Migrated a Java 8 monolith to a microservices architecture using \textbf{Java 17} and \textbf{Spring Boot}, ensuring scalability and maintainability;
            \item[--] Implemented unit and integration tests, and documented APIs with \textbf{Swagger};
            \item[--] Executed tasks using the \textbf{SCRUM} methodology and implemented \textbf{CI/CD} pipelines in GitLab;
            \item[--] Containerized services with \textbf{Docker}, simplifying environment deployments;
            \item[--] Technologies: \textbf{Java 17, Spring Boot, Oracle, JUnit, Swagger, Postman, JSF, Docker}.
        \end{itemize}
    \end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Full Stack Developer} & \hfill Jan. 2022 - Dec. 2023 \\
\textbf{- ZDoc - Document Management Technology}  & \hfill Aracaju, SE\\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Maintained legacy ERP with \textbf{HTML, CSS, PHP 7 and jQuery};
        \item[--] Migrated ERP to new technologies using \textbf{React} and \textbf{Laravel} integrated with \textbf{Oracle};
        \item[--] Managed tasks, versioning, and deployments with \textbf{Trello} and \textbf{GitLab};
        \item[--] Applied TDD for code coverage using the \textbf{PHPUnit} library;
        \item[--] Technologies: \textbf{PHP, jQuery, Laravel, MySQL, React, REST, JIRA}.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Full Stack Developer} & \hfill Sep. 2021 - Jan. 2022 \\
\textbf{- Pueri Health}  & \hfill Aracaju, SE\\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] Prototyped an \textbf{MVP} solution for a startup incubation program;
        \item[--] Deployed the application to the \textbf{Heroku} cloud platform;
        \item[--] Documented APIs with \textbf{Swagger} and implemented unit tests with \textbf{JUnit};
        \item[--] Technologies: \textbf{Java 17, Spring Boot, Thymeleaf, Bootstrap, Swagger, Heroku, PostgreSQL}.
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{lXr}	
2021 - 2027 & Bachelor's in Computer Science at \textbf{Federal University of Sergipe (UFS)} & Aracaju-SE \\\\

2020 - 2022 & Continuous Training for Web Programmers at \textbf{Federal Institute of Paraíba (IFPB)} & Pedras de Fogo-PB \\ 
\end{tabularx}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[--] \textbf{Programming languages}: Java (Spring Boot, JUnit), PHP (Laravel, PHPUnit), JavaScript, TypeScript, Go, Python, C;
        \item[--] \textbf{Frontend}: React, Angular, SenchaJS, jQuery, Thymeleaf, Bootstrap, HTML, CSS;
        \item[--] \textbf{Backend}: Spring Boot, Django, Laravel, PHP 7, JSF, REST and SOAP APIs;
        \item[--] \textbf{Databases}: PostgreSQL, MySQL, Oracle, with SQL query optimization;
        \item[--] \textbf{DevOps}: Docker, Docker Compose, Git, GitLab CI/CD, Nginx Proxy Manager, Heroku;
        \item[--] \textbf{Integrations}: \textbf{Tax systems (NF-e, NFC-e)}, ERPs (Bluesoft, C5), and external services via APIs;
    \end{itemize}
    \end{minipage}
}
\end{tabularx}

%----------------------------------------------------------------------------------------
% CERTIFICATES
%----------------------------------------------------------------------------------------
\section{Languages and Certificates}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Google Cybersecurity Professional Certificate} & \hfill Coursera, Jul. 2025 \\ 
\textbf{Linux Fundamentals} & \hfill FIAP, Dec. 2021 \\
\textbf{TQI Java Developer} & \hfill DIO, Dez. 2021 \\
\textbf{English B2 TOEFL ITP} & \hfill ISF, Nov. 2017 \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}
\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Hacktoberfest 2021} & \hfill \href{https://github.com/sicpjs/estrutura-e-interpretacao-de-programas-de-computador-javascript}{Translation on GitHub} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
    Participated in the translation of the book \emph{"Structure and Interpretation of Computer Programs in JavaScript"} from English to Portuguese as part of the open-source community during Hacktoberfest 2021.
}  \\
\end{tabularx}

\vfill
\center{\footnotesize Last Update: September 10, 2025}

\end{document}
